---
title: "Performance test"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Performance_test}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning=F, message=F}
library(CampNetworkSimulator)
library(ggplot2) # for plotting
```

In this vignette we are simply testing the time-to-completion of our code as a function of network size. We will be using 3 cores for the network diagnostics and the network simulation steps and all other default parameters will be left unchanged. We will also be running 3 simulations for each network size as this is closer to how this model would actually be used (for statistical confidence).

```{r echo= T, results = 'hide'}
network_sizes = c(100, 500, 1000, 3000, 5000, 10000, 20000)
time_to_completion = sapply(
  network_sizes,
  function(size){
    # return elapsed time to run simulation a given net size
    system.time(net_simulate(n = size))[3]
  })
```

```{r, out.width='100%', dpi=500}
ggplot(data.frame(sizes = network_sizes, times = time_to_completion),
       aes(x = sizes, y = times))+
  geom_point()+
  theme_bw()+
  xlab('Network size/Number of nodes')+
  ylab('Execution time (in seconds)')
```







