---
title: "Visualization"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Visualization}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message=F, warning=F}
library(CampNetworkSimulator)
```

A few plotting functions are provided though many more could be used, and we encourage making more custom plots from the results dataframe.

The user may choose to plot the default curves representing the number of individual in each state (susceptible, infected, quarantined...) at each time step using `plot_states()`:
```{r}
plot_states(net_example)
```

_Usage:_
```{r, eval = F}
net_obj = net_simulate()
plot_states(net_obj)
```

Additionally, we offer a couple of function to visualise the contact matrix at one or at each timestep of the simulation. The code below shows the contact matrix at time step 5 of the simulation. 

```{r}
network.heatmap(net_example, at = 5)
```

Additionally, we can extract a GIF of this interaction matrix in a range or from beginning to end.

```{r}
network.heatmap.GIF(net_example) # from first time-step to end
```

```{r}
network.heatmap.GIF(net_example, interval = 5:10) # from timestep 5 to timestep 10
```

_Note:_ In the contact matrix, a black square (a value of 1) at represents an interaction between the 'row' individual and the 'column' individual.


